Typing a linear \picalc

### 2020-04-27 paper/paper.tex
Clarify substitution diagrams

      \draw[->] (gamma-l) -- node[above] {$\vdash P$} (xi-l);
      \draw[->] (xi-l) -- node[above] {$\vdash Q$} (psi-l);
      \draw[->,densely dotted] (gamma-r) -- node[below] {$\vdash \subst{P}{j}{i}$} (xi-r);
      \draw[->,densely dotted] (xi-r) -- node[below] {$\vdash \subst{Q}{j}{i}$} (psi-r);
      \draw[->,densely dotted] (xi-l) -- node[left] {$\ni_i l$} (theta);
      \draw[->,densely dotted] (xi-r) -- node[left] {$\ni_j l$} (theta);
    \end{tikzpicture}
    \caption{
      Diagrammatic representation of the generalized substitution for process input.
      Thanks to the additional premise in Remark \ref{re:delta-zero}, we know that $m$ is at least capable of $n$, i.e. $\opsquared{m}{\delta}{n}$ for some $\delta$.
    }
    \label{fig:subst}
  \end{subfigure}
  \hspace{\fill} % DO NOT LEAVE EMPTY LINE
  \begin{subfigure}{.4\textwidth}
    \centering
    \begin{tikzpicture}
      \node (gamma-l) at (0,4)   {};
      \node (gamma-m) at (0,2)   {};
      \node (gamma-r) at (0,0)   {};
      \node (xi-l)    at (2,5)   {};
      \node (xi-m)    at (2,3.5) {};
      \node (xi-r)    at (2,2)   {};
      \node (psi-m)   at (4,3.5) {};

      \draw[->] (gamma-l) -- (xi-r);
      \draw[->] (gamma-m) -- (xi-r);
      \draw[->] (gamma-r) -- (xi-r);
      \draw[->] (gamma-l) -- (gamma-m);
      \draw[->] (gamma-r) -- (gamma-m);
      \draw[->] (xi-l)    -- (xi-m);
      \draw[->] (xi-r)    -- (xi-m);
      \draw[->] (xi-l)    -- (psi-m);
      \draw[->] (xi-m)    -- (psi-m);
      \draw[->] (xi-r)    -- (psi-m);
    \end{tikzpicture}
    \caption{
      Alternative approach without the $\ni_i n$ and $\ni_j n$ arrows.
      These are not strictly necessary, but they make the inductive hypotheses compositional.
      Without them, framing lemmas would have to be used extensively.
    }
    \label{fig:subst-compositionality}
  \end{subfigure}
\end{figure}

>>>>

      \draw[->] (gamma-l) -- node[above] {$\vdash P$} (xi-l);
      \draw[->] (xi-l) -- node[above] {$\vdash Q$} (psi-l);
      \draw[->,densely dotted] (gamma-r) -- node[below] {$\vdash \subst{P}{j}{i}$} (xi-r);
      \draw[->,densely dotted] (xi-r) -- node[below] {$\vdash \subst{Q}{j}{i}$} (psi-r);
      \draw[->,densely dotted] (xi-l) -- node[left] {$\ni_i l$} (theta);
      \draw[->,densely dotted] (xi-r) -- node[left] {$\ni_j l$} (theta);
    \end{tikzpicture}
    \caption{
      Diagrammatic representation of the inductive substitution lemma.
      Continuous lines represent known facts, dotted lines proof obligations.
      From $\Delta_i = \ell_{\o}$, we can deduce that there exists some $\delta$ such that $\opsquared{m}{\delta}{n}$.
      From that, we can find first $\ni_i l$ and then $\ni_j l$, splitting the diagram across its vertical axis, making it possible to inductively derive both $\vdash \subst{P}{j}{i}$ and $\vdash \subst{P}{j}{i}$.
    }
    \label{fig:subst}
  \end{subfigure}
  \hspace{\fill} % DO NOT LEAVE EMPTY LINE
  \begin{subfigure}{.4\textwidth}
    \centering
    \begin{tikzpicture}
      \node (gamma-l) at (0,4)   {};
      \node (gamma-m) at (0,2)   {};
      \node (gamma-r) at (0,0)   {};
      \node (xi-l)    at (2,5)   {};
      \node (xi-m)    at (2,3.5) {};
      \node (xi-r)    at (2,2)   {};
      \node (psi-m)   at (4,3.5) {};

      \draw[->] (gamma-l) -- (xi-r);
      \draw[->] (gamma-m) -- (xi-r);
      \draw[->] (gamma-r) -- (xi-r);
      \draw[->] (gamma-l) -- (gamma-m);
      \draw[->] (gamma-r) -- (gamma-m);
      \draw[->] (xi-l)    -- (xi-m);
      \draw[->] (xi-r)    -- (xi-m);
      \draw[->] (xi-l)    -- (psi-m);
      \draw[->] (xi-m)    -- (psi-m);
      \draw[->] (xi-r)    -- (psi-m);
    \end{tikzpicture}
    \caption{
      Alternative approach without arrows $\ni_i n$ and $\ni_j n$.
      These are not strictly necessary, but they ease the composition of the inductive hypotheses.
      Without them, framing lemmas would have to be used extensively.
    }
    \label{fig:subst-compositionality}
  \end{subfigure}
\end{figure}
